The Adaptive Multiscale Simulation Infrastructure -- Core Features and Multi-scale Soft Tissue Simulation

### 2017-12-11 doc/articles/amsi_overview/amsi_overview.tex
working on the amsi paper

\title{The Adaptive Multiscale Simulation Infrastructure -- Core Features and Biological Tissue Simulation Feature Utilization}
\author{W.R. Tobin, D. Fovargue, V.W.L. Chan, M.S. Shephard}
\date{\today}
\documentclass[11pt]{article}
\bibliographystyle{siam}

@@

\label{amsi_scales}
Individual scales in a simulation are declared during the initialization of the simulation, follow by the determination and asignment of RankSets to scales, guided by a supplied configuration file or user-implemented algorithm. Scale-coupling relations are also declared at initialization time, though this decleration is limited to the indication that two scale may interact at some point during the simulation, and nothing more.

>>>>

\title{The Adaptive Multiscale Simulation Infrastructure -- Core Features and Multi-scale Soft Tissue Simulation}
\author{W.R. Tobin, V.W.L. Chan, M.S. Shephard}
\date{\today}
\documentclass[11pt]{article}
\bibliographystyle{siam}

@@

\label{amsi_scales}
Individual scales in a simulation are declared during the initialization of the simulation, follow by the determination and assignment of RankSets to scales, guided by a supplied configuration file or user-implemented algorithm. Scale-coupling relations are also declared at initialization time, though this decleration is limited to the indication that two scale may interact at some point during the simulation, and nothing more.
